Weather Data Integration and Assimilation System\\

### 2020-02-10 lit/sec_1-fews.tex
Updated lit review introduction

There are many of Weather forecasting, assimilation and dissemination systems developed by some of developed countries around the world as a result of trying to reduce the damage causing by natural disasters such as flood, storms, hurricanes, and even for drought.
Such natural disasters heavily affected on the economy and the life conditions of the country, researchers have developed systems and many of these systems are using as proprietary systems. Other countries also using those systems and adopt with own version of system which effective for the specific weather condition in a particular country.
This chapter \ref{ch:literature} presents a Literature review on existing systems and their architecture approach and design with available resources.
In Section \ref{se:fews}, we present Most influenced systems for \acrshort{wdias} is \acrshort{fews}. \acrfull{lead}, \db{an open data handling platform distributed as closed-source software, is presented in Section \ref{se:lead}}. \acrshort{lead} is following the \acrfull{soa} for system architecture.
Under each system we explore both system architecture, scalability and flexibility of the system.

\dbc{Complete above while referring to all major sections with chapter.}

>>>>

There are many of Weather forecasting, assimilation and dissemination systems developed by some of developed countries around the world as a result of trying to reduce the damage causing by natural disasters such as flood, storms, hurricanes, and even for drought.
Such natural disasters heavily affected on the economy and the life conditions of the country, researchers have developed systems and many of these systems are using as proprietary systems. Other countries also using those systems and adopt with own version of system which effective for the specific weather condition in a particular country.
This chapter \ref{ch:literature} presents a Literature review on existing systems and their architecture approach and design with available resources.
In Section \ref{se:fews}, we present most influenced systems for \acrshort{wdias} is \acrshort{fews}. \acrfull{lead}, an open data handling platform distributed as closed-source software, is presented in Section \ref{se:lead}. \acrshort{lead} is following the \acrfull{soa} for system architecture. In Section \ref{se:dias}, we discussed about \acrfull{dias} which is developed by Japanese, and support as a common data platform other than weather data. \acrfull{madis} is another widely use data integration system, which also provide data access with quality control, and we discuss in the last Section \ref{se:madis}.
Under each system we explore both system architecture, scalability and flexibility of the system.
